How explicit is the Explicit Formula?

### 2013-01-05 talk.tex
deleting trailing whitespace

\begin{frame}
 \vskip40pt {\Large  Equivalently, putting:\begin{itemize} \item $\gamma_E(p)=0$ if $p$ is a bad or supersingular prime for $E$ and\vskip20pt \item $\gamma_E(p)= -1$ if $E$ has more than $p+1$  ${\bf F}_p$-rational points, and \vskip20pt \item $\gamma_E(p) = +1$ if less.\end{itemize}}\end{frame}\begin{frame}\vskip20pt
{\Large \vskip40pt 
 So:\vskip20pt
   $$\Delta_E(X): =\sum_{p\le X}\gamma_E(p).$$

 More generally we might consider  weighting functions $p \mapsto g_E(p)$ that have the property that }  \end{frame}\begin{frame}\vskip20pt
{\Large \vskip40pt 
\begin{itemize} \item for all primes $p$, $g_E(p)$ is an {\it odd} function of the value  $a_E(p)$, and \vskip20pt \item the {\it sum\ of\ local\ data}  $$\delta_E(X):=\sum_{p\le X}g_E(p)$$ has---or can be convincingly conjectured to have---a finite  {\it mean}.\end{itemize}}\end{frame}
%\end{document}
\begin{frame}\vskip20pt
{\Large \vskip40pt 
Any such  $$p \mapsto  g_E(p)$$ represents a version of a `bias race'.
\vskip20pt
To illustrate specific features of the `Explicit Formula' we focus on three examples of such races for an elliptic curve $E$. }\end{frame}
  %\end{document}
\begin{frame}\vskip20pt
{\Large  \vskip20pt  Form  these 'sums of local data' ---\vskip20pt

>>>>

\begin{frame}
 \vskip40pt {\Large  Equivalently, putting:\begin{itemize} \item $\gamma_E(p)=0$ if $p$ is a bad or supersingular prime for $E$ and\vskip20pt \item $\gamma_E(p)= -1$ if $E$ has more than $p+1$  ${\bf F}_p$-rational points, and \vskip20pt \item $\gamma_E(p) = +1$ if less.\end{itemize}}\end{frame}

\begin{frame}
   $$\Delta_E(X): =\sum_{p\le X}\gamma_E(p).$$

\end{frame}

\begin{frame}
 More generally we might consider  weighting functions $p \mapsto g_E(p)$ that have the property that }  \end{frame}

\begin{frame}\vskip20pt
{\Large \vskip40pt
\begin{itemize} \item for all primes $p$, $g_E(p)$ is an {\it odd} function of the value  $a_E(p)$, and \vskip20pt \item the {\it sum\ of\ local\ data}  $$\delta_E(X):=\sum_{p\le X}g_E(p)$$ has---or can be convincingly conjectured to have---a finite  {\it mean}.\end{itemize}}\end{frame}
%\end{document}
\begin{frame}\vskip20pt
{\Large \vskip40pt
Any such  $$p \mapsto  g_E(p)$$ represents a version of a `bias race'.
\vskip20pt
To illustrate specific features of the `Explicit Formula' we focus on three examples of such races for an elliptic curve $E$. }\end{frame}
  %\end{document}
\begin{frame}\vskip20pt
{\Large  \vskip20pt  Form  these 'sums of local data' ---\vskip20pt
